\begin{itemize}
\item[(a)]
	Assume \(H\) is not collision resistant. \\
	This means finding \(x_0 \neq x_1\) so that \(H^{s_0 \vert\vert s_1}(x_0) = H^{s_0 \vert\vert s_1}(x_1)\) is possible with non-negl. probability. \\
	\(H^{s_0 \vert\vert s_1}(x_0) = H^{s_0 \vert\vert s_1}(x_1) \Leftrightarrow H^{s_0}_0(H^{s_1}_1(x_0)) = H^{s_0}_0(H^{s_1}_1(x_1)) \) \\
	Define \(H^{s_1}_1(x_0) = y_0\) and \(H^{s_1}_1(x_1) = y_1\). \\
	For \(H^{s_0 \vert\vert s_1}(x_0) = H^{s_0 \vert\vert s_1}(x_1)\) to have a collision either \(y_0 = y_1 = y\) \\
	which makes  \(H^{s_0}_0(y_0) = H^{s_0}_0(y_1) = H^{s_0}_0(y)\) trivially true because \(H^{s_0}_0\) gets the same input \\
	or \(H^{s_0}_0(y_0) = H^{s_0}_0(y_1)\) with \(y_0 \neq y_1\) \\
	\\
	If \(H_0\) is collision resistant but \(H_1\) not, then the probability of finding \(x_0 \neq x_1\) so that \(H^{s_1}_1(x_0) = H^{s_1}_1(x_1) = y\) is non-negl. \\
	Since \(H_0\) gets the same input \(y\) in this case the probability for a collision for \(H\) is the same as for \(H_1\) and is non-negl.\\
	\(\Rightarrow H\) is not collision resistant.\\

\item[(b)]
	Assume \(H\) is not collision resistant. \\
	This means finding \(x_0 \neq x_1\) so that \(H^{s_0 \vert\vert s_1}(x_0) = H^{s_0 \vert\vert s_1}(x_1)\) is non-negl. \\
	\(H^{s_0 \vert\vert s_1}(x_0) = H^{s_0 \vert\vert s_1}(x_1) \Leftrightarrow H^{s_0}_0(x_0) \vert\vert H^{s_1}_1(x_0) = H^{s_0}_0(x_1) \vert\vert H^{s_1}_1(x_1) \) \\
	We know that at least one \(H_i\) \(i \in \{0,1\}\) is collision resistant per definition. \\
	\par
	\begingroup
	\leftskip1.5em
	\rightskip\leftskip
		Assume \(H_0\) is collision resistant but \(H_1\) is not, making finding \(x_0 \neq x_1\) so that \(H^{s_1}_0(x_0) = H^{s_1}_0(x_1)\) is negl. \\
		If \(H^{s_1}_1(m) = c\) with \(c\) being a constant value for all \(m\) then \(H^{s_0 \vert\vert s_1}(m) = H^{s_0}_0(m) \vert\vert c\)\\
		This produces a string with the same collision resistance propability as \(H_0\) since only a constant string \(c\) is added at the end.\\
		If \(H_1\) is some other function, the collision probability becomes even smaller since there are even more different strings produceable this way.\\ 
		\\
		Assuming \(H_1\) is collision resistant but \(H_0\) is not, has the same result since it doesn't matter if the collision resistant part is added at first or 				second. \\
	\par
	\endgroup
	\(\Rightarrow\) contradiction: \(H\) can't be non-negl. since it has to have at least the collision resistant propablility as the collision resistant  \(H_i\) \(i \in \{0,1\}\) which is negl. \\
	\(\Rightarrow H\) is collision resistant.\\

\item[(c)] 
	\(H'(m) = H^{c(m)}(r(m))\) with \(m\) of the format \(0^n1\vert\vert x\) and \(c(m) = n\) and \(r(m) = x\). \\
	Since \(H^n\) is the \(n\)-times application of \(H\) we can construct the following attack on this Hash function to break the collision resistance: \\
	\(H^{n}(x) = y_0\) as one random example and \\ 
	\(H^1(y_0) = y_1\) \\
	We use \(x_0 = 0^{n + 1}1 \vert\vert x\) and \(x_1 = 01 \vert\vert y_0\) since\\
	\(H'(x_0) = H^{c(x_0)}(r(x_0)) = H^{n+1}(x) = H^1(H^n (x)) = H^1(y_0) = H^{c(x_1)}(r(x_1)) = H'(x_1)\). \\
	\(\Rightarrow H\) is not collision resistant.\\
	
\end{itemize}  
  